Hyperopt-Sklearn: Subtitle?

### 2014-04-26 papers/2014-automl/paper.tex
updating graphics
removing unused graphics
paper - more writing

In total, our parameterization had 62 hyperparameters: 6 for preprocessing and 56 for classification.
How many boolean: XXX
How many categorical: XXX
How many discrete: XXX
How many real-valued: XXX
It is important to note that although the total number of hyperparameters is large, the number of {\em active} hyperparameters describing any one model is much smaller: a model consisting of \texttt{PCA} and a \texttt{RandomForest} for example,
would have only 12 active hyperparameters (1 for the choice of preprocessing, 2 internal to PCA, 1 for the choice of classifier and 8 internal to the RF).
Hyperopt description language allows us to differentiate between {\em conditional} hyperparameters (which must always be assigned) and {\em non-conditional} hyperparameters (which may remain unassigned when they would be unused).
We make use of this mechanism extensively so that Hyperopt's search algorithms do not waste time learning by trial and error that e.g. RF hyperparameters have no effect on SVM performance.
Even within a single classifier, there were instances of conditional parameters: \texttt{KNN} has conditional parameters depending on the distance metric,
and \texttt{LinearSVC} has 3 binary parameters (``loss'', ``penalty'', and ``dual'') that admit only 4 valid joint assignments.
We also included a blacklist of (preprocessing, classifier) pairs that did not work together, e.g. PCA and MinMaxScaler were incompatible with MultinomialNB, TF-IDF could only be used for text data, and the tree-based classifiers were not
compatible with the sparse features produced by the TF-IDF preprocessor.

/ classifier
There are also bl
Allowing for a 10-way discretization of real-valued hyperparameters, and taking these conditional hyperparameters into account, a grid search of our search space would require an infeasible number of evalutions (on the order of $10^{12}$).

% TALK ABOUT THE FIT/PREDICT API AND OUR FIT DOES SEARCH?

\section{Experiments}

\begin{figure}
    \centering
    %\includegraphics[width=2.90in]{lda_boxplots}
    %\includegraphics[width=2.90in]{svm_boxplots}\\
    %\includegraphics[width=2.90in]{branin_boxplots}
    %\includegraphics[width=2.90in]{har6_boxplots}
    \caption{
        Each boxplot shows the distribution of minimum values found by each algorithm on 10 randomized runs. (Lower is better)
    }
    \label{fig:boxplots}
%\vspace{-3em}
\end{figure}

@@

\subsection{Acknowledgements*}

>>>>

In total, our parameterization had 62 hyperparameters: 6 for preprocessing and 56 for classification.
How many boolean: XXX
How many categorical: XXX
How many discrete: XXX
How many real-valued: XXX
It is important to note that although the total number of hyperparameters is large, the number of {\em active} hyperparameters describing any one model is much smaller: a model consisting of \texttt{PCA} and a \texttt{RandomForest} for example,
would have only 12 active hyperparameters (1 for the choice of preprocessing, 2 internal to PCA, 1 for the choice of classifier and 8 internal to the RF).
Hyperopt description language allows us to differentiate between {\em conditional} hyperparameters (which must always be assigned) and {\em non-conditional} hyperparameters (which may remain unassigned when they would be unused).
We make use of this mechanism extensively so that Hyperopt's search algorithms do not waste time learning by trial and error that e.g. RF hyperparameters have no effect on SVM performance.
Even within a single classifier, there were instances of conditional parameters: \texttt{KNN} has conditional parameters depending on the distance metric,
and \texttt{LinearSVC} has 3 binary parameters (``loss'', ``penalty'', and ``dual'') that admit only 4 valid joint assignments.
We also included a blacklist of (preprocessing, classifier) pairs that did not work together, e.g. PCA and MinMaxScaler were incompatible with MultinomialNB, TF-IDF could only be used for text data, and the tree-based classifiers were not
compatible with the sparse features produced by the TF-IDF preprocessor.
Allowing for a 10-way discretization of real-valued hyperparameters, and taking these conditional hyperparameters into account, a grid search of our search space would still require an infeasible number of evalutions (on the order of $10^{12}$).

Following Scikit-learn's convention, hyperopt-sklearn provides an \texttt{Estimator} class with a \texttt{fit} method and a \texttt{predict} method.
The \texttt{fit} method of this class performs hyperparameter optimization, and after it has completed, the \texttt{predict} method applies the best model to test data.
Hyperopt makes it possible to parallelize the model search over a cluster, with communication handled via a MongoDB instance.
Each evaluation during optimization performs training on a large fraction of the training set, estimates test set accuracy on a validation set, and returns that validation set score to the optimizer.
At the end of search, the best configuration is retrained on the whole data set to produce the classifier that handles subsequent \texttt{predict} calls.

\section{Experiments}
We conducted experiments on three data sets to establish that hyperopt-sklearn can find accurate models on a range of data sets
hyperopt-sklearn finds accurate models,
%(b) different data sets lead hyperopt-sklearn to select different models, and
(c) search can be carried out in a reasonable amount of time.
Results were collected on three data sets: MNIST, 20-Newsgroups, and Convex Images.
MNIST~\citep{lecun+bottou+bengio+haffner:1998} is a well-known data set of 70K $28\times 28$ greyscale images of hand-drawn digits.
20-Newsgroups is a 20-way classification data set of 20000 newsgroup messages (we did not remove the headers for our experiments)~\citep{20newsgroups}.
Convex Images~\citep{larochelle+etal:2007} is a binary classification task of distinguishing pictures of convex white-colored regions in small ($32\times 32$) black-and-white images.

To establish that searching the full space is effective,
we performed optimization runs of up to 300 function evaluations searching either the entire space, or else subspaces that corresponded to specific classifier types.
We used three optimization algorithms in Hyperopt: random search, annealing, and TPE.
Figure~\ref{fig:avg_test_scores} shows that the performance of the model found from throughout the entire search space was not statistically inferior to the best model pulled from each classifier subspace;
there was no penalty for keeping all options open during search.
Table~\ref{tbl:opt_scores} lists the test set scores of the best models found by cross-validation, as well as some points of reference from previous work.
Hyperopt-sklearn's scores are relatively good on each data set, indicating that with hyperopt-sklearn's parameterization, Hyperopt's optimization algorithms are competitive with human experts.

%To support the hypothesis that the search carried out by hyperopt-sklearn is necessary for good performance on a range of data sets, we present three pieces of evidence.
%First, looking again at Figure~\ref{fig:avg_test_scores}, note that 
%Figure~\ref{fig:pies} shows that 
%different data sets lead hyperopt-sklearn to select

\begin{figure}
    \centering
    \includegraphics[width=2.90in]{AverageTestScoresClassifier}
    \caption{
        For each data set, searching the full configuration space (``Any Classifier'') delivered performance approximately on par with a search that was restricted to the best classifier type.
        (Best viewed in color.)
    }
    \label{fig:avg_test_scores}
%\vspace{-3em}
\end{figure}

@@

%\subsection*{Acknowledgements}
